Large Linear Multi-output Gaussian Process Learning

### 2017-04-04 paper/paper.tex

We build multi-output GP models as instances of general GPs, where a multi-output GP model identifies correlations between outputs through a shared input space \cite{alvarez2011kernels}.

>>>>

We build multi-output GP models as instances of general GPs, where a multi-output GP model identifies correlations between outputs through a shared input space \cite{alvarez2012kernels}.
